\documentclass{bioinfo}
\copyrightyear{2010}
\pubyear{2010}
\usepackage{natbib}
\usepackage[english]{babel}

\newcommand\caret{\mathbin{\char`\^}}

\usepackage{sidecap}

\DeclareOldFontCommand{\tt}{\normalfont\ttfamily\footnotesize}{}

\begin{document}
\firstpage{1}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\title[Proteomatic -- a platform for MS/MS data evaluation]
{Proteomics to go: Proteomatic enables the user-friendly creation of versatile MS/MS data evaluation workflows}
\author[Michael Specht \textit{et~al.}]
{Michael~Specht\footnotemark[1], 
Mia~Terashima, 
Sebastian~Kuhlgert,
Christian~Fufezan,
Bianca~Naumann-Busch,
Ricarda~H\"ohner and
Michael~Hippler
}
\address{Institute of Plant Biology and Biotechnology, University of 
M\"unster, Germany}

\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

\editor{Associate Editor: XXXXXXX}

\maketitle

\footnotetext[1]{Correspondence to: Michael Specht, 
Institute of Plant Biology and Biotechnology, Hindenburgplatz 55,
D-48161 M\"unster, Germany. E-mail: 
michael.specht@uni-muenster.de}

\renewcommand{\thefootnote}{\arabic{footnote}}

\begin{abstract}

\section{Motivation:}


Mass spectrometric methods and corresponding software tools for data evaluation
are evolving rapidly.
Programming expertise is required to create an automated pipeline in which
several programs are run in succession.
A graphical user interface (GUI) to programs is crucial for widespread
deployment.
If descriptions for these programs were available, GUIs could be created
automatically, providing widgets to change parameters.
Furthermore, using information about input and output files, several programs 
could be combined into a processing pipeline.

\section{Results:}

We present Proteomatic, an operating system-independent and user-friendly 
proteomics data evaluation platform that enables the construction and execution 
of MS/MS data evaluation pipelines using free software. 
The necessary programs for peptide identification and quantitation are 
downloaded automatically. 
Due to a strict separation of functionality and presentation, new programs
can be added easily.
Additionally, we introduce qTrace, a novel tool for the large-scale quantitation 
of metabolically labeled samples in full scans.
We demonstrate a fully functional MS/MS pipeline which allows for peptide
and protein identification, validation and quantitation based on metabolic 
labeling using OMSSA for peptide identification and qTrace for quantitation.

\section{Availability:}

Proteomatic is released under the LGPL.
Source code and installers for Windows, Mac OS X, and Linux are 
freely available at http://www.proteomatic.org.

\section{Contact:} 
michael.specht@uni-muenster.de
\end{abstract}

\input{maintext}

\section*{Acknowledgement}

We would like to thank Susan Hawat for conducting the mass spectrometric 
measurements and Ingrid Jan{\ss}en for testing and valuable user feedback.

{\em Funding:} 
This work was supported by
Deutscher \mbox{Akademischer} Austauschdienst [A/06/70349 to M.T.]; 
Deutsche Forschungsgemeinschaft [FU780/2-1 to C.F.]; 
and Bundesministerium f\"ur Bildung und Forschung [0315265C to M.H.].

\bibliographystyle{natbib}
\bibliography{Proteomatic}

\end{document}
